%--------------------------------------------------------------------------------
% Author :      Bhavyai Gupta
% Repository:   https://github.com/zbhavyai/zbhavyai.github.io.git
% Website:      https://zbhavyai.github.io
%--------------------------------------------------------------------------------

\documentclass[a4paper]{article}

%--------------------------------------------------------------------------------
% Page layout and margins
\usepackage{fullpage}                                                   % Reasonable default margins
\usepackage[left=0.5in, right=0.5in, bottom=0.3in, top=0.3in]{geometry} % Custom margin setup
\pagestyle{empty}                                                       % Suppress page numbers

%--------------------------------------------------------------------------------
% Mathematics and symbols
\usepackage{amsmath}                                                    % Core math environments and symbols
\usepackage{amssymb}                                                    % Extra math symbols
\usepackage{textcomp}                                                   % Extra text symbols (like \textdegree)

%--------------------------------------------------------------------------------
% Typography and spacing
\usepackage[protrusion=true, expansion=false]{microtype}                % Fine-tune font spacing
\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

\usepackage{fontspec}
\setmainfont{AdwaitaSans}[
    Path=./fonts/,
    Extension = .ttf,
    UprightFont=*-Light,
    BoldFont=*-Bold,
    ItalicFont=*-Italic,
    BoldItalicFont=*-BoldItalic
    ]

\newfontfamily\defaultserif{Latin Modern Roman}

%--------------------------------------------------------------------------------
% Text formatting and justification
\usepackage{ragged2e}                                                   % Enable text justification
\usepackage{ulem}                                                       % Allow underlining, strike-through, etc.
\raggedright                                                            % Left-align text

%--------------------------------------------------------------------------------
% Hyperlinks and color
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}                   % Enable and color hyperlinks
\usepackage[dvipsnames]{xcolor}                                         % Extended color support
\definecolor{Accent}{HTML}{1A4F80}                                      % Define a custom accent color

%--------------------------------------------------------------------------------
% Custom symbols and bullets
\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }                  % Define a custom bullet


%--------------------------------CUSTOM COMMANDS---------------------------------
\newcommand{\header} [1] {
    \vspace{6pt}
    {\hspace*{-18pt} \textcolor{Accent}{\large\textbf{\MakeUppercase{#1}}}}
    \vspace{-7pt} \\
    {\color{Accent}\hspace*{-18pt} \hrulefill \hspace*{-7pt}}
    \vspace{3pt}
}

\newcommand{\resumeHeadingExperience}[4]{
    \textbf{#1} \hfill {#2}\\
    {#3} \hfill {#4}\\
    \vspace{-7pt}
}

\newcommand{\resumeItemExperience}[1]{
  \item{
    \begin{justify}
    \setlength{\rightskip}{0.15in}{{\fontsize{9.0pt}{11pt}\selectfont #1} \vspace{-2pt}}
    \end{justify}
  }
}

\newcommand{\resumeHeadingProject}[3]{
    {\textbf{#1}} (\href{#2}{\uline{source code}})
    \vspace{-5pt}
}

\newcommand{\resumeItemProject}[1]{
  \item{
    \begin{justify}
    \setlength{\rightskip}{0.15in} {{\fontsize{9.0pt}{11pt}\selectfont #1} \vspace{-4pt}}
    \end{justify}
  }
}

\newcommand{\resumeHeadingEducation}[4]{
    \textbf{#1} \hfill {#2}\\
    {\fontsize{9.0pt}{11pt}\selectfont {#3}} \hfill {#4}\\
    \vspace{5pt}
}

%----------------------------------RESUME START----------------------------------
\begin{document}


%------------------------------------HEADING-------------------------------------
\begin{center}
   {\defaultserif {\Huge\bfseries BHAVYAI GUPTA}}
\end{center}
\vspace{-10pt}

\begin{center}
    \href{mailto:zbhavyai@gmail.com}{\uline{zbhavyai@gmail.com}} \quad|\quad
    \href{tel:+15875756982}{\uline{+1 (587) 575-6982}} \quad|\quad
    \href{https://linkedin.com/in/zbhavyai}{\uline{linkedin.com/in/zbhavyai}} \quad|\quad
    \href{https://zbhavyai.github.io}{\uline{Portfolio Website}}
\end{center}


%------------------------------------SUMMARY-------------------------------------
\header{Professional Summary}

\vspace{-9pt}
\begin{justify}
{\fontsize{9.0pt}{11pt}\selectfont GCP-certified Backend Software Engineer with 6+ years of experience building scalable microservices and secure cloud-native platforms using Java, Quarkus, Spring Boot, and GCP. Proven track record in automating infrastructure, reducing operational costs, and leading cross-functional teams. Strong focus on API design, observability, and AI-driven backend automation in enterprise environments.}
\end{justify}
\vspace{-4pt}


%--------------------------------TECHNICAL SKILLS--------------------------------
\header{Technical Skills}

{\fontsize{9.0pt}{11pt}\selectfont
\begin{tabular}{ l l }
    \textbf{Backend}    & Java, Python, Quarkus, Spring Boot, JPA, Hibernate, JUnit, REST API, Microservices    \\
    \textbf{Frontend}   & React.js, TypeScript, JavaScript, Bootstrap, HTML, CSS                                \\
    \textbf{Databases}  & PostgreSQL, MySQL, SQL, Flyway                                                        \\
    \textbf{DevOps}     & Docker, Git, CI/CD, Linux, Ansible, Bash, Maven, Prometheus, Grafana, Nginx           \\
    \textbf{Cloud}      & GCP Certified, Google Cloud, Compute Engine, Cloud Run, Functions, Pub/Sub, Storage   \\
    \textbf{Security}   & Keycloak, HashiCorp Vault, SSO, OIDC, OAuth2, JWT                                     \\
    \textbf{Workflow}   & GitHub, Bitbucket, Jira, Agile, Scrum, Kanban                                         \\
\end{tabular}
}

%-----------------------------------EXPERIENCE-----------------------------------
\header{Relevant Work Experience}

\resumeHeadingExperience {Userful Corporation} {Calgary, Canada} {Tech Lead} {Apr 2022 - Present}

\begin{itemize} \itemsep 2pt
    \resumeItemExperience {Currently the leading development of \textbf{edge-based AI analysis} using LangChain and Vision-Language Models on \textbf{Azure IoT Edge} to automate dashboard and data \textbf{analysis and incident reporting}.}
    \resumeItemExperience {Architected a unified credential management system for integrating tools like Power BI, Tableau, ServiceNow, etc, \textbf{eliminating 90\% of manual logins} across 100+ sources per site. Developed API-driven dashboard selection and configuration interfaces, enabling \textbf{zero-touch visualizations with 24/7 uptime}.}
    \resumeItemExperience {Engineered \textbf{system observability} (using DBus, Micrometer, Grafana, Prometheus) and dynamic alerting to users (via in-app notifications and emails), \textbf{reducing mean time to detection} by 80\%.}
    \resumeItemExperience {Achieved \textbf{\$100,000 in annual savings} by customizing and whitelabeling Grafana v7.5.15 source code, eliminating OEM licensing costs.}
    \resumeItemExperience {Designed and maintained resilient \textbf{disaster recovery system}, automating daily backups and on-demand restoration for PostgreSQL databases, Vault secrets, and gigabytes of media files.}
    \resumeItemExperience {Drove Agile delivery cycles through sprint planning, backlog refinement, and peer code reviews. \textbf{Mentored junior developers} via onboarding and technical guidance. Authored documentation adopted across teams as the internal standard.}
\end{itemize}


%------------------------------------PROJECTS------------------------------------
\header{Projects}

\resumeHeadingProject {BudLib} {https://github.com/budlib} {Jan 2022 - Apr 2022}
\begin{itemize}
    \resumeItemProject {Built a full-stack library management system using \textbf{Spring Boot, React, and MySQL}, replacing legacy software and streamlining book inventory and loan workflows.}
    \resumeItemProject {Delivered a production-ready system with a \textbf{RESTful backend, user authentication, and dynamic frontend views}. Still actively used by the school librarian.}

\end{itemize}

\resumeHeadingProject {Inspirational Morning} {https://github.com/zbhavyai/inspirational-morning} {Jun 2024 - Jun 2024}
\begin{itemize}
    \resumeItemProject {Designed and deployed a \textbf{serverless} Java application on \textbf{Google Cloud Run Functions} to send automated daily inspirational quotes to Google Chat using ZenQuotes API and \textbf{event-driven Pub/Sub triggers}.}
    \resumeItemProject {Implemented cloud-based scheduling with \textbf{Google Cloud Scheduler} and dynamic timezone support, enabling configurable weekday message delivery for Google Workspace users.}
\end{itemize}

\resumeHeadingProject {Fedora Setup} {https://github.com/zbhavyai/fedora-setup} {May 2025 - May 2025}
\begin{itemize}
    \resumeItemProject {Automated my Fedora Workstation setup using Ansible, drastically \textbf{reducing manual configuration time} from hours to minutes.}
    \resumeItemProject {Configured essential packages, system settings, dev tools, and GNOME shell customizations, demonstrating expertise in \textbf{infrastructure as code} and \textbf{system automation}.}
\end{itemize}
\vspace{3pt}

%---------------------------------CERTIFICATIONS---------------------------------
\header{Certifications}

\textbf{Associate Cloud Engineer} \hfill Nov 2024 - Nov 2027\\
{\fontsize{9.0pt}{11pt}\selectfont \href{https://www.credly.com/badges/52bb681c-f535-47e7-b669-78e9b4d7c4a0}{\uline{Google Cloud Certified}}}
\vspace{4pt}


%-----------------------------------EDUCATION------------------------------------
\header{Education}

\resumeHeadingEducation {University of Calgary} {Calgary, Canada} {MEng Software Engineering} {May 2021 - Apr 2022}
\resumeHeadingEducation {Delhi Technological University} {Delhi, India} {BTech Electronics and Communication} {Aug 2012 - Aug 2016}


%-----------------------------------RESUME END-----------------------------------
\end{document}
