%--------------------------------------------------------------------------------
% Author :      Bhavyai Gupta
% Repository:   https://github.com/zbhavyai/zbhavyai.github.io.git
% Website:      https://zbhavyai.github.io
%--------------------------------------------------------------------------------

\documentclass[a4paper]{article}

\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{textcomp}
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}
\usepackage{ulem}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\textheight=10in
\pagestyle{empty}
\raggedright
\usepackage[left=0.8in,right=0.8in,bottom=0.3in,top=0.8in]{geometry}

% Support text justify
\usepackage{ragged2e}

% Slightly tweak font spacing to prevent hyphenation after text justify
\usepackage{microtype}

% Color the heading
\usepackage[dvipsnames]{xcolor}
\definecolor{Accent}{HTML}{1A4F80}

\microtypesetup{protrusion=true,expansion=true}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% Generate pdf is ATS parsable
\input{glyphtounicode}
\pdfgentounicode=1


%--------------------------------CUSTOM COMMANDS---------------------------------
\newcommand{\lineunder} {
    \vspace*{0pt} \\
    {\color{Accent}\hspace*{-18pt} \hrulefill \hspace*{-6pt}} \\
}

\newcommand{\header} [1] {
    \vspace*{3pt}
    {\hspace*{-18pt} \textcolor{Accent}{\large\textbf{\textsc{#1}}}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\resumeHeadingExperience}[4]{
    \textbf{#1} \hfill {#2}\\
    \textit{#3} \hfill {#4}\\
    \vspace{-3mm}
}

\newcommand{\resumeItemExperience}[2]{
  \item{
    \begin{justify}
    \setlength{\rightskip}{0.15in} \textbf{#1}{: #2 \vspace{-2pt}}
    \end{justify}
  }
}

\newcommand{\resumeHeadingProject}[3]{
    {\textbf{#1}} $|$ \textit{#2} % \hfill {#3}
    \vspace{-2mm}
}

\newcommand{\resumeItemProject}[1]{
  \item{
    \begin{justify}
    \setlength{\rightskip}{0.15in} {#1 \vspace{-4pt}}
    \end{justify}
  }
}

\newcommand{\resumeHeadingEducation}[4]{
    \textbf{#1} \hfill {#2}\\
    {#3} \hfill {#4}\\
    \vspace{2mm}
}

%----------------------------------RESUME START----------------------------------
\begin{document}
\vspace*{-40pt}


%------------------------------------HEADING-------------------------------------
\vspace*{-10pt}
\begin{center}
    \textbf{\Huge \scshape {Bhavyai Gupta}}\\
\end{center}
\vspace{-10pt}

\begin{center}
    \href{mailto:zbhavyai@gmail.com}{\uline{zbhavyai@gmail.com}} \quad|\quad
    \href{tel:+15875756982}{\uline{+1(587)575-6982}} \quad|\quad
    \href{https://linkedin.com/in/zbhavyai}{\uline{linkedin.com/in/zbhavyai}} \quad|\quad
    \href{https://zbhavyai.github.io}{\uline{Portfolio Website}}
\end{center}
\vspace{5pt}


%--------------------------------TECHNICAL SKILLS--------------------------------
\header{Technical Skills}

\vspace{2pt}
\begin{tabular}{ l l }
    \textbf{Backend}    & Java, Python, Quarkus, Spring Boot, JPA, Hibernate, JUnit, REST API, Microservices    \\
    \textbf{Frontend}   & React.js, TypeScript, JavaScript, HTML, CSS, Bootstrap                                \\
    \textbf{Databases}  & PostgreSQL, MySQL, SQL, Flyway                                                        \\
    \textbf{DevOps}     & Docker, Git, CI/CD, Linux, Ansible, Bash, Maven, Prometheus, Grafana, Nginx           \\
    \textbf{Cloud}      & GCP Certified, Google Cloud (Compute Engine, Cloud Run, Functions, Pub/Sub, Storage)  \\
    \textbf{Security}   & HashiCorp Vault, Keycloak, SSO, OIDC, OAuth2, JWT                                     \\
    \textbf{Workflow}   & GitHub, Bitbucket, Jira, Agile, Scrum, Kanban                                         \\
\end{tabular}
\vspace{2mm}


%-----------------------------------EXPERIENCE-----------------------------------
\header{Work Experience}

\resumeHeadingExperience {Userful Corporation} {Calgary, Canada} {Software Developer} {Apr 2022 - Present}
\begin{itemize} \itemsep 1pt
    \resumeItemExperience {Data integration and visualization} {Led the integration of various BI and data visualization tools, including Power BI, Tableau, Epic Systems, ServiceNow, Grafana, PowerPoint, and Domo, utilizing a centralized credential management for secure and seamless user access.}
    \resumeItemExperience {Robust data management} {Designed and implemented a comprehensive backup and restore system for PostgreSQL databases, Vault secrets, and media files.}
    \resumeItemExperience {Monitoring \& alerting} {Integrated real-time metrics from DBus into our core product using Micrometer, Prometheus, and Grafana, implementing notifications to alert users of critical system usage.}
    \resumeItemExperience {Grafana whitelabeling} {Whitelabeled Grafana v7.5.15 source code, resulting in cost savings of approximately \$100,000 by avoiding OEM licensing.}
    \resumeItemExperience {High-performance rendering} {Leveraged Nvidia SLI Mosaic technology to enable 4K output and integrated Megapixel products for 8K content routing on LED panels with centralized control.}
    \resumeItemExperience {Enhanced security} {Integrated HashiCorp's Vault to secure critical media sources, including RTSP streams, VNC/RDP connections, and BI platforms.}
\end{itemize}

\resumeHeadingExperience {Luxoft} {Singapore} {Consultant} {Oct 2018 - Dec 2019}
\begin{itemize} \itemsep 1pt
    \resumeItemExperience{Market Risk} {Led the technical build for Murex Market Risk migration from version 2.36 to 3.41, utilizing ANT scripts, bash scripts, and configuration management for seamless transition.}
\end{itemize}

\resumeHeadingExperience {Capgemini} {Singapore} {Associate Consultant} {Aug 2017 - Aug 2018}
\begin{itemize} \itemsep 1pt
    \resumeItemExperience{Market Risk} {Built the Market Risk module within MX.3, adapting to diverse client and international entity requirements.}
\end{itemize}

\resumeHeadingExperience {Capgemini} {Gurugram} {Associate Consultant} {Jun 2016 - Aug 2017}
\begin{itemize} \itemsep 1pt
    \resumeItemExperience{Market Risk} {Implemented a greenfield market risk framework, encompassing scenario generation, application, and computations like VaR, Stress Testing, and Back Testing.}
\end{itemize}


%------------------------------------PROJECTS------------------------------------
\header{Projects}

\resumeHeadingProject {BudLib} {Spring Boot, React.js, MySQL} {Jan 2022 - Apr 2022}
\begin{itemize}
    \resumeItemProject {Full-stack web application developed and used by Calgary Waldorf School for library management.}
\end{itemize}

\resumeHeadingProject {IntelliNurse} {Spring Boot, React.js, MySQL} {Feb 2022 - Mar 2022}
\begin{itemize}
    \resumeItemProject {Full-stack web application for Registered Nurses to post articles and surveys, achieving 2nd place in a hackathon.}
\end{itemize}

\resumeHeadingProject {Inspirational Morning} {Quarkus, Google Cloud functions, Google Chat webhook} {Jun 2024 - Jun 2024}
\begin{itemize}
    \resumeItemProject {Serverless function using Quarkus and Google Cloud to send daily inspirational quotes to Google Chat.}
\end{itemize}

\resumeHeadingProject {Fedora Setup} {Ansible} {May 2025 - May 2025}
\begin{itemize}
    \resumeItemProject {Automated set up of Fedora Workstation using Ansible, including installation of essential packages, configuration of various system and application settings, and customization of the GNOME shell.}
\end{itemize}


%---------------------------------CERTIFICATIONS---------------------------------
\header{Certifications}
\textbf{Associate Cloud Engineer} \hfill Nov 2024 - Nov 2027\\
\href{https://www.credly.com/badges/52bb681c-f535-47e7-b669-78e9b4d7c4a0}{\uline{Google Cloud Certified}}
\vspace{2mm}


%-----------------------------------EDUCATION------------------------------------
\header{Education}

\resumeHeadingEducation {University of Calgary} {Calgary, Canada} {MEng Software Engineering} {May 2021 - Apr 2022}
\resumeHeadingEducation {Delhi Technological University} {Delhi, India} {BTech Electronics and Communication} {Aug 2012 - Aug 2016}


%-----------------------------------RESUME END-----------------------------------
\
\end{document}
